---
title: Quarto-manuscript01  
subtitle: Reproduction  
authors:
  - name: Robert C. Cline, Sr.
    affiliation: Golden Triangle Land Services, Inc.
    roles: writing
    email: rccline@fastmail.fm  
    corresponding: true
bibliography: references.bib
--- 

## Quarto manuscripts:  https://quarto.org/docs/manuscripts  

### Slides
* mine.quarto.pub/quarto-manuscdripts-rmed  
* github.com/mine-cetinkaya-rundel/quarto-manuscrpts-rmed   

### Manuscript: 
* mine-cetinkaya-rundel.github.io/indo-rct   
* github.com/mine-cetinkaya-rundel/indo-rct   



## Section

This is a simple placeholder for the manuscript's main document [@knuth84]. Mine Certinkaya-Rundel presented a webinar on the steps to create a Quarto-Manuscript on March 24, 2024 [@rconsortiumMedicineQuartoReproducible2024][^1]

[^1]: C.f. YouTube presentation *https://www.youtube.com/watch?v=NK1onTLcgY4&t=1265s*

## Study outcomes

{{< embed notebooks/incidences.qmd#fig-incidences-adverse-events >}}

```{r}
#| label: penguin_bodymass

library(palmerpenguins)
# data(penguins)
mean_bodymass <- base::round(mean(penguins$body_mass_g, na.rm = TRUE), 2)
```

**This is an example of inline code**:\
The mean body mass of penguins is `r mean_bodymass` grams.\
What if we use a label (@penguin_bodymass) 

 


**Cross-referencing**

-   This is a cross-reference to our (@fig-incidences-adverse-events).\
-   You can also bring up the *cross-reference-insert-anything tool* by typing:

## Citations  

In Visual mode: Insert citation or, control-shift-F8 [@hennekens1996]

This is a sample citation from a paper published in 2012 which you can find at: https://pubmed.ncbi.nlm.nih.gov/8929364/ DOI: 10.1056/NEJM199611283352207

Reference for (@fig-incidences-adverse-events). Citation: [@elmunzer2012]

```{r eval=FALSE}
# See 30 minutes into youtube video for discussion of embedding 
# See 36 minutes for cross referencing 
# See 38 minutes, citations  
```


## Quarto use binder

* In the terminal: quarto use binder  
* Takes a bit of time for the virtual environment being built.
* Edit in Rstudio  


**Note**: a git clone distributee merely runs *quarto render index.qmd* to generate the quarto files that were listed as .quarto/ in the .gitignore file. 

## Add .github reference  

**To create a .github folder** in your project directory and *set up your Quarto manuscript to reference the GitHub repository upon rendering*, you can follow these steps:

**Create the .github Folder**:

Open your project directory in your file explorer.
Right-click within the directory and choose "New Folder" or create a new folder named *.github*.

**Add Necessary Files**:

1. **publish.yml* 
Inside the .github folder, create a new file named workflows (without an extension).
In this workflows folder, create a YAML file with a name like ***publish.yml***. You can name it anything, but it's common to name it after the action it performs or the tool it configures.

2. Open the *publish.yml* file in a text editor and add the necessary configuration for your workflow. Below is an example of how you might configure it to reference your GitHub repository: 

----------------------------------------------------------------------
`
name: Quarto Render

on:  
->  push:  
->->    branches:  
->->->      - master  

jobs:  
->  render:  
->->    runs-on: ubuntu-latest  
->->    steps:  
->->->      - name: Checkout Repository  
->->->        uses: actions/checkout@v2  
->->->      - name: Render Quarto Manuscript  
->->->        run: quarto render  

`
-------------------------------------------------------------------

## freeze in *Yaml* _quarto.yml*  
47 minutes  

execute:
  freeze: auto  
  
* freeze 
  - unless I have explicitly touched a qmd file, do not rerun the code in it 
  - *freeze: false* -  means always rerun the code

## References

```{r eval=FALSE}

library(knitr)
library(quarto)


quarto::quarto_render("index.qmd", output_format = "html")
# quarto::quarto_render("index.qmd", output_format = "pdf")

# cannot render plos-pdf.  See video 28 minutes. 
# quarto::quarto_render("index.qmd", output_format = "plos-pdf")

```
